A Static Checked Interface and a Checker for Tezos Smart Contracts

### 2022-09-30 reports/proposal/proposal.tex
updated

\section{A Static Checked Programming Interfect}
\label{sec:checked-programming-interfect}
A Michelson contract may fail due to a programming condition caused by the FAILWITH statement. It terminates contract execution with an error message reported back to the caller. These conditions can be considered as preconditions for calling a smart contract in conjunction with an entrypoint. It is indeed expensive to invoke a contract and then find that it fails. Fortunately, some of these failures can be predicted by performing a static check before invocation.

@@

Our work is related to the Tezos blockchain, which supports Michelson as a low-level contract language, and the OCaml language, which has an expressive polymorphic type system and a powerful module system that we extend with contract modules. We propose a symbolic execution model for Michelson that allows us to guarantee secure invocations of a contract on the blockchain. The model allows us to formulate preconditions and postconditions, and then specify invariants and constraints that are used to guarantee a safe invocation. We can also use the model to constrain the possible invocation sequences of entrypoints. The specification is checked against the contract implementation by symbolic execution. When a smart contract is invoked, the invocation can be checked against these invariants and constraints before it is used in the chain, where the invocation may be succeed. The checking of invariants and constraints can be done with an SMT solver such as the Z3 solver and its library in Ocaml.

In the end, we would like to provide a platform that automatically generates the Contract module from a given smart contract specification in Michelson. The contract module guarantees a type-safe interaction and handles the error returned on a failed call. And it guarantees a safe invocation (or prevent a failed invocation) by statically checking the correctness of the invocation before deployment.
\section{A Static Checker for Tezos Smart Contracts}
\label{sec:static-checker}
Verification of a smart contract is important because its implementation cannot be changed once it is deployed. However, there is not yet a sufficient tool to help developers of Tezos smart contracts to formally verify the contract. Therefore, another goal of our research is to develop a verification tool, a checker, for Michelson smart contracts. When a smart contract script is passed along with the specification of properties, the tool statically checks whether these properties are satisfied. In fact, symbolic execution could play the main role in checking properties. We first provide a domain-specific language (DSL) in which the user can specify the properties. The property specifications are then converted into formulas in Z3 in Ocaml, which are then checked against the smart contract implementation using symbolic execution.

>>>>

\section{A Static Checked Programming Interfect}
\label{sec:checked-programming-interfect}
A Michelson contract may fail due to a programming condition caused by the FAILWITH statement. The execution of the contract is reported back to the caller with an error message. These conditions can be considered as a precondition for calling a smart contract in conjunction with an entrypoint. It is indeed expensive to invoke a contract and then find that it fails. Fortunately, some of these failures can be predicted by performing a static check before invocation.

@@

Our work is related to the Tezos blockchain, which supports Michelson as a low-level contract language, and the OCaml language, which has an expressive polymorphic type system and a powerful module system that we extend with contract modules. We propose a symbolic execution model for Michelson that allows us to guarantee secure invocations of a contract on the blockchain. The model allows us to formulate preconditions and postconditions, and then specify invariants and constraints that guarantee a safe invocation. We can also use the model to constrain the possible invocation sequences of entrypoints. The specification is checked against the contract implementation by symbolic execution. When a smart contract is invoked, the invocation can be checked against these invariants and constraints before being used in the chain, where the invocation can succeed. Checking invariants and constraints can be done with an SMT solver like the Z3 solver and its library in Ocaml.

In the end, we would like to provide a platform that automatically generates the Contract module from a given smart contract specification in Michelson. The contract module guarantees a type-safe interaction and handles the error returned on a failed call. And it guarantees a safe invocation (or prevents a failed invocation) by statically checking the correctness of the invocation before deployment.
\section{A Static Checker for Tezos Smart Contracts}
\label{sec:static-checker}
Verification of a smart contract is important because its implementation cannot be changed once it is deployed. However, there is not yet a sufficient tool to help developers of Tezos smart contracts to formally verify the contract. Therefore, another goal of our research is to develop a verification tool, a checker, for Michelson smart contracts. When a smart contract script is passed along with the specification of properties, the tool statically checks whether these properties are satisfied. In fact, symbolic execution could play the main role in checking properties. We first provide a domain-specific language (DSL) in which the user can specify the properties. The property specifications are then converted into formulas in Z3 in Ocaml, which are then checked against the smart contract implementation using symbolic execution.
